RNAseq aCRY processing

### 2024-04-17 1_data_processing/1_data_processing.Rmd
counts figures upload

# Plot
par(mar=c(2,4,0,0)+.1) # set margins for figure
plot(sample_table_all$mappingrates)
# -> boring

@@

### Deseq2 acry
```{r}
design <- ~condition
# design <- ~genotype+treatment+genotype:treatment

@@

##########################################\n
## filter all rows with rowsum = 0 ####
par(mfrow=c(1,2))
hist(log(counts(dds)), breaks=100, ylim = c(0,11000), xlim = c(0,10))
hist(counts(dds), breaks=1000000, ylim = c(0,100000), xlim = c(0,10))
# -> dip at log(counts(dds)=2-3)
par(mfrow=c(1,1))

>>>>

# Plot
par(mar=c(2,4,0,0)+.1) # set margins for figure
plot(m.table$mappingrates)
# -> boring

@@

### Deseq2 acry
```{r dds_acry}
design <- ~condition
# design <- ~genotype+treatment+genotype:treatment

@@

##########################################\n
# filter all rows with rowsum = 0 ####
par(mfrow=c(1,2))
hist(log(counts(dds)), breaks=100, ylim = c(0,11000), xlim = c(0,10))
hist(counts(dds), breaks=1000000, ylim = c(0,100000), xlim = c(0,10))
# -> dip at log(counts(dds)=2-3)
par(mfrow=c(1,1))
